Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-08 paper/paper.tex
cool ref

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
observations and rewards \citep{aronov2017}.
These simulations would be used to update the value function, without ever looking inside the black box describing the model's dynamics. This would be a simple control algorithm by evaluating all legal actions and selecting the action with
highest expected cumulative rewards.
In POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief-based state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Much recent work points to Monte Carlo or stochastic sampling-based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. \textbf{XXX Elvis: refs needed in last sentence.} For sampling-based methods it is still almost non-existent beyond the description of receptive fields. \textbf{XXX Elvis: rephrase last sentence}

>>>>

In the human brain,
the HC could contribute to synthesizing imagined sequences of world states,
observations and rewards \citep{aronov2017, chao2017interaction}.
These simulations would be used to update the value function, without ever looking inside the black box describing the model's dynamics. This would be a simple control algorithm by evaluating all legal actions and selecting the action with
highest expected cumulative rewards.
In POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief-based state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Much recent work points to Monte Carlo or stochastic sampling-based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines. \textbf{XXX Elvis: refs needed in last sentence.} For sampling-based methods it is still almost non-existent beyond the description of receptive fields. \textbf{XXX Elvis: rephrase last sentence}
